### 2016-05-18 w-wires/paper_gerasimovda.tex
more stuff for paper

@@

We know that $s(k)$ is bounded by $1$ from above in the upper complex plane  ($\Im k \ge 0$) \todo{why?}, hence $\ln \abs{\det S} \le 0$. \todo{we might have to do something about the singularity at $k=1$}

@@

@@

\[
s_4(x + \iu y) = 
\begin{cases}
\frac{s_1(Z_0)}{Z_0 - Z} (x - Z) &, Z < y \le Z_0 \\
s_1(Z_0) &, y > Z_0
\end{cases}
\]

>>>>

We'll use the inequality:

\[
\frac{x}{1 + x} \le \ln(1 + x)
\]
, which holds for $-1 < x \le 0$. % As $x$ goes to $-1$,

We'll rewrite it in a more convenient form by a substitution $x \to s(k) - 1$:

\[
1 - \frac{1}{s(k)} \le \ln s(k)
\]

Since $s(k)$

@@

We know that $s(k)$ is bounded by $1$ from above in the upper complex plane  ($\Im k \ge 0$) \todo{why?}, hence $\ln \abs{\det S} \le 0$.

@@

$s_3(k)$ helps us to deal

@@

\[
s_4(x + \iu y) = 
\begin{cases}
\frac{s_1(Z_0)}{Z_0 - Z} (y - Z) &, Z < y \le Z_0 \\
s_1(Z_0) &, y > Z_0
\end{cases}
\]

\subsection*{Proof of convergence for constant part}
\todo{Might be easier in Cayley space}

\subsection*{Proofs of convergence for logarithmic parts}
\todo{DO NOT FORGET ABOUT shifted circle!!! $k = R \eexp{\iu t} + \iu C(R)$}

\todo{For second, we could probably get rid of $\frac{1}{(k-1)^2}$ via the minimum estimation}

\todo{For first, things are slightly harder. Prove about generic function with zero at $Z$, then first implies second???}
Peak induced by $k=1$ is quite nasty. Ensure it converges, implement a checker. Although, it might not, it probably gets smoothed by $\abs{\det S} = 1$ for the original function....

\todo{Use some inequalities involving logarithms???}
% http://dlmf.nist.gov/4.5

\todo{Unit cicle in Cayley space maps to $R$, and $\ln\abs{\det S}$ on $R$ is zero everywhere}
